The CrypTool Script: \\ Mathematics and Cryptography \\ \vspace{30pt} {\large Background reading\\*[-8pt] for the free elearnig program CrypTool (version 1.3.10)} \vspace{60pt}

### 2005-07-04 script/en/chapters/introduction.tex
Update - Bernhard Esslinger June 2005

% --------------------------------------------------------------------------
\section*{Preface to the 6th Edition of the CrypTool Script}  \addcontentsline{toc}{section}{Preface to the 6th Edition of the CrypTool Script}

@@

This edition of the script mainly updates the summaries of the following 
topical research areas:
\vspace{-7pt}
\begin{itemize}
  \item the search for the largest prime numbers (generalized Mersenne 
        and Fermat primes) \\ 
%        and Fermat primes, ``M-40'') 
	(chap. \ref{spezialzahlentypen}, \ref{zahlentyp_mersenne}), 
  \item progress in number theory (``Primes in P'') (chap. \ref{PrimesinP}), 
  \item the factorisation of big numbers (TWIRL, RSA-160)\index{TWIRL device} 
        (chap. \ref{TWIRLDevice}, \ref{RSA-160}),
  \item progress in cryptanalysis of the AES standard 
        (chap. \ref{NeueAES-Analyse}) and
  \item progress in brute-force attacks against symmetric algorithms 
        (chap. \ref{Brute-force-gegen-Symmetr}).\index{Attack!brute-force}
\end{itemize}

Chapter 5 (more about hash algorithms) and chapter 6 (now we explain in
greater detail how elliptic curves are defined over different number
fields) of this script have also been enhanced.

\vspace{12pt}
The first time the document was delivered with CrypTool\index{CrypTool} 
was in version 1.2.01. Since then it has been expanded and revised in every 
new version of CrypTool (1.2.02, 1.3.00, 1.3.02, 1.3.03 and now 1.3.04).

I'd be more than happy if this also continues in the further open-source
versions of CrypTool\index{CrypTool} (they will be delivered by the University
of Darmstadt).

@@

Hofheim, May 2003

@@

Chapters 4 and 6 require a deeper knowledge in mathematics, while the
other chapters should be understandable with a school leaving certificate.

@@

CrypTool\index{CrypTool} was developed during the end-user awareness program
at Deutsche Bank in order to increase employee awareness of IT security and provide them with
a deeper understanding of the term security.
A further aim has been to enable users to understand the cryptographic
procedures. In this way, using CrypTool
as a reliable reference implementation of the various encryption procedures
(because of using the industry-proven Secude Library\index{Secude}),
you can test the encryption implemented in other programs. \par \vskip + 3pt

@@

At this point I'd like to thank explicitly 3 people who particularly 
contributed to CrypTool\index{CrypTool}. Without their talents and engagement 
CrypTool would not be what it is today:
\vspace{-7pt}
\begin{itemize}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org Cornelius Schneider and
   \item Dr.\ Peer Wichmann.
\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\

>>>>

% --------------------------------------------------------------------------
\section*{Preface to the 7th Edition of the CrypTool Script}
\addcontentsline{toc}{section}{Preface to the 7th Edition of the CrypTool Script}

@@

This edition of the script adds some topics, but mainly updates areas (e.g. the
summaries of topical research areas):
\vspace{-7pt}
\begin{itemize}
  \item the search for the largest prime numbers (generalized Mersenne 
        and Fermat primes) \\ 
%        and Fermat primes, ``M-40'') 
	(chap. \ref{spezialzahlentypen}, \ref{zahlentyp_mersenne}), 
  \item the factorisation of big numbers (RSA-200)\index{RSA-200} 
        (chap. \ref{RSA-200}),
  \item progress in cryptanalysis of hash algorithms 
        (chap. \ref{collision-attacks-against-sha-1}),
  \item progress in ideas for new crypto methods (RSA successor) 
        (chap. \ref{xxxxxxxxxBrute-force-gegen-Symmetr})\index{xxxxxxxxxxxxxxxx} and
  \item a list, in which movies or novels cryptography or number theory has a 
        major role (see appendix \ref{s:appendix-movies}).
\end{itemize}

\vspace{12pt}
The first time the document was delivered with CrypTool\index{CrypTool} 
was in version 1.2.01. Since then it has been expanded and revised in almost every 
new version of CrypTool (1.2.02, 1.3.00, 1.3.02, 1.3.03, 1.3.04 and now 1.3.10).

I'd be more than happy if this also continues in the further open-source
versions of CrypTool\index{CrypTool}.

@@

Frankfurt (Germany), June 2005

@@

Chapters  \ref{Chapter_ModernCryptography} (Modern Cryptography) and 
\ref{Chapter_EllipticCurves} (Elliptic Curves) require a deeper knowledge
in mathematics, while the other chapters should be understandable with a 
school leaving certificate.

@@

CrypTool\index{CrypTool} was developed during the end-user awareness program
at Deutsche Bank in order to increase employee awareness of IT security and provide them with
a deeper understanding of the term security.
A further aim has been to enable users to understand the cryptographic
procedures. In this way, using CrypTool
as a reliable reference implementation of the various encryption procedures
(because of using the industry-proven Secude library\index{SECUDE IT Security}),
you can test the encryption implemented in other programs. \par \vskip + 3pt

@@

At this point I'd like to thank explicitly six people who particularly 
contributed to CrypTool\index{CrypTool}. Without their special talents
 and engagement CrypTool would not be what it is today:
\vspace{-7pt}
\begin{itemize}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org-Cornelius Schneider
   \item Dr.\ Peer Wichmann
   \item Prof. Dr. Claudia Eckert,  Mr.\ Thomas Buntrock and Mr.\ Thorsten Clausius.
\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\

### 2005-07-04 script/en/chapters/menus.tex
be update
be updates
Update - Bernhard Esslinger June 2005

\pagebreak
\enlargethispage{1cm}
\section{CrypTool Menus}
\hypertarget{appendix-menutree}{}\label{s:appendix-menutree}
This appendix contains the complete menu tree of CrypTool. 
Please notice that not all menu items are always available, because the
menu tree is built up dynamically: which menu items are available depends
on the type of the currently active document window.
The brute-force analysis for DES e.~g. is only available, if the active
window is opened in the hexadecimal view. On the other hand the menu item
``Generate Random Numbers\dots'' is always available. 
Within the figures \ref{menu-detail-1} and \ref{menu-detail-2} 
this relation is shown in the brackets after the menu items,
e.~g. ``Find\dots[ATH]'' means, that the function ``Find\dots'' is only
available for ASC-, text- and hexadecimal windows.
\begin{center}
\begin{tabular}{rl}
\bf Code letter & \bf Type of document \\
M & (no document opened)\\
A & ASC\\
T & Text\\
H & Hexadecimal\\
P & Plot\\
\end{tabular}
\end{center}

\nobreak

\begin{figure}[!hb]
\begin{center}
%\frame{
\includegraphics[scale=1.1, clip, viewport=0 300 404 591]{figures/cryptool-menu-detail-en}
%}
\caption{Detailed view of the CrypTool menu tree -- part 1}
\label{menu-detail-1}
\end{center}
\end{figure}

\begin{figure}[b]
\begin{center}
%\frame{
\includegraphics[scale=1.1, clip, viewport=404 117 828 598]{figures/cryptool-menu-detail-en}
%}
\caption{Detailed view of the CrypTool menu tree -- part 2}
\label{menu-detail-2}
\end{center}
\end{figure}
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{
\includegraphics[scale=0.75, angle=270, viewport=14 5 829 590]{figures/cryptool-menu-en}
%}
\caption{Complete overview of the CrypTool menu tree} 
\label{menuoverview}
\end{center}
\end{figure}
\clearpage

>>>>

\newpage
\hypertarget{appendix-start}{}\label{s:appendix-start}

\section{Appendix}

\hyperlink{appendix-menutree}{(Appendix A: CrypTool Menu Tree)}

\hyperlink{appendix-authors}{(Appendix B: CrypTool Script Authors)}

\hyperlink{appendix-movies}{(Appendix C: Movies and Literature with Relation to Cryptography)}

%\pagebreak
\newpage
\enlargethispage{1cm}
\subsection{CrypTool Menus}
\hypertarget{appendix-menutree}{}\label{s:appendix-menutree}

This appendix contains the complete menu tree of CrypTool\index{CrypTool} version 1.3.10.

Which menu items are active (that is not greyed), depends on the type 
of the currently active document window.
The brute-force analysis\index{Attack!brute-force} for DES e.~g. is only
available, if the active window is opened in the hexadecimal view. 
On the other hand the menu item
``Generate Random Numbers\dots'' is always available.

The following types of documents exist in CrypTool:
\begin{center}
\begin{tabular}{rl}
\bf Code letter & \bf Type of document \\
A & ASC\\
T & Text\\
H & Hexadecimal\\
P & Plot\\
\end{tabular}
\end{center}

%\nobreak
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{
\includegraphics[scale=0.75, angle=270, viewport=14 72 835 590]{figures/cryptool-menu-en}
%viewport=rand-links? rand-unten breite hoehe? [bezogen auf querformat]
%}
\caption{Complete overview of the CrypTool menu tree} 
\label{menuoverview}
\end{center}
\end{figure}
\clearpage

### 2005-07-04 script/en/chapters/moderncryptography.tex
ecc + ds changes
be updates
Update - Bernhard Esslinger June 2005

\newpage
%**************************************************************************************************************************
\section{The Mathematical Ideas behind Modern Cryptography}
(Oyono R. / Esslinger B., Sep. 2000, Updates Nov. 2000, Feb. 2003)
\subsection{One way functions with trapdoor and complexity classes}
\index{Cryptography!modern} \index{One way function} \hypertarget{OneWayFunktion1}{}
A {\bf one way function} is a function that can be calculated 
efficiently, but whose inverse is extremely complicated and practically 
impossible to calculate.\par

@@

%--------------------------------------------------------------------
\subsubsection{Merkle-Hellman knapsack encryption}
%--------------------------------------------------------------------
\index{Hellman Martin} \index{Merkle Ralph}

@@

In 1982, \index{Shamir Adi} Shamir \cite{Shamir1982} specified an algorithm for 
breaking the system in polynomial \index{Polynomial} time without solving the general knapsack 
problem. Len \index{Adleman Leonard} Adleman \cite{Adleman1982} and Jeff 
Lagarias \index{Lagarias Jeff} \cite{Lagarias1983} specified an algorithm for 
breaking the twice iterated Merkle-Hellman knapsack encryption procedure in 
polynomial time. Ernst Brickell \index{Brickell Ernst} \cite{Brickell1985} then 
specified an algorithm for breaking multiply iterated Merkle-Hellman knapsack 
encryption procedures in polynomial time. This made this procedure unsuitable as 
an encryption procedure. It therefore delivers a one way function whose trapdoor 
information (defamiliarisation of the 0-1 knapsack problem) could be discovered 
by an evesdropper.

@@

%--------------------------------------------------------------------
\subsubsection[The RSA procedure]
{The RSA procedure\footnotemark}
\footnotetext{
Using CrypTool\index{CrypTool} v1.3 you gain practical experience
with the RSA procedure via the menu {\bf Indiv.Procedures \textbackslash{} 
RSA Demonstration \textbackslash{} RSA Cryptosystem}.
}
\index{RSA} \hypertarget{RSAVerfahren}{} 
As early as 1978, R. \index{Rivest Ronald} Rivest, \index{Shamir Adi} A. Shamir,  \index{Adleman Leonard} L. Adleman \cite{RSA1978} introduced 
the most important asymmetric cryptography procedure to date.  \par

@@

In this case it has been shown that the procedure \index{Rabin Michael O.} 
\index{Rabin!public key procedure} is equivalent to breaking the factorisation problem. 
Unfortunately, this procedure is susceptible to chosen-cipher text attacks.
\index{Attack!chosen-cipher text}
\begin{center}
\fbox{\parbox{12cm}{        
Let $ p $ and $ q $ be two different prime numbers with $ p,q\equiv 3 \mod 4 $ 
and $ n = pq.$ Let $ 0\leq B \leq n-1.$ \\
\underline{Public key:}
\[ e=(n,B). \]
\underline{Private key:}
\[ d=(p,q). \]
\underline{Encryption:}
\[ y= e_{T} (x) = x(x+B) \mod n.\]
\underline{Decryption:}
\[ d_{T} (y) = \sqrt{y + B^2/4} -B/2 \mod n. \]
}}
\end{center}

@@

    \subsubsection{The discrete logarithm in $ \Z_p $}
Let $ p $ be a prime number and let $ g \in \Z_p^\ast=\{0,1,\ldots,p-1\} $. Then 
the discrete exponential function base $ g $  is defined as
\[ e_g : k \longrightarrow y:=g^k \mod p, \quad 1\leq k \leq p-1. \]
The inverse function is called a discrete logarithm function $ \log_g $; the 
following holds:
\[ \log_g (g^k) =k. \]
\index{Exponential function!discrete} The problem of the discrete logarithm (in 
$ \Z_p^\ast$) is understood to be as follows:
\[ {\rm Given~ } p,g {\rm ~and~ } y, {\rm~determine~} k {\rm ~such~that~ } 
y=g^k \mod p {\rm .}\]
It is much more difficult to calculate the discrete logarithm than to evaluate 
the discrete exponential function (see chapter \ref{MultOrdPrimitveRoot}).
There are several procedures for calculating the discrete logarithm 
\cite{4Stinson1995}\index{Stinson 1995}:
\vskip + 5pt
\begin{center}
\begin{tabular}{|l|l|}\hline
Name                 &        Complexity \\ \hline \hline
Baby-Step-Giant-Step &         $ O(\sqrt{p}) $ \\ \hline
Silver-Pohlig-Hellman    &    polynomial in $ q, $ the greatest \\
&  prime factor of $ p-1. $ \\ \hline
Index-Calculus &             $ O(e^{(1+o(1)) \sqrt{\ln (p) \ln (\ln (p))}}) $ \\ 
\hline
\end{tabular}
\end{center}
\vskip +5 pt
\index{Silver} \index{Pohlig} \index{Hellman Martin}

%--------------------------------------------------------------------
\subsubsection[Diffie-Hellman key agreement]
{Diffie-Hellman key agreement\footnotemark}
\footnotetext{%
With CrypTool\index{CrypTool} v1.3.04  this exchange protocol has been
visualized: you can execute the single steps with concrete numbers using 
menu {\bf Indiv. Procedures \textbackslash{} Diffie-Hellman Demonstration}.
}

\index{Key agreement (key exchange)!Diffie-Hellman} 
\index{Diffie Whitfield}
\index{Hellman Martin}
\index{Diffie-Hellman}

@@

%--------------------------------------------------------------------
\subsubsection{ElGamal public key encryption procedure in $ \Z_p^\ast$}
%--------------------------------------------------------------------
\index{ElGamal!public key}
By varying the Diffie-Hellman key agreement protocol \index{Diffie-Hellman} 
\index{Encryption!El Gamal public key} slightly, you can obtain an 
asymmetric encryption algorithm. This observation was made by Taher ElGamal.
\begin{center}
\fbox{\parbox{12cm}{        
Let $ p $ be a prime number such that the discrete logarithm in $ \Z_p $ is 
difficult to compute. Let $ \alpha \in \Z_p^\ast $ be a primitive element. Let $a \in \N$ and $ 
\beta = \alpha^{a}  \mod p. $\\
\underline{Public key:}
\[ p,\alpha,\beta. \]
\underline{Private key:}
\[a. \]
Let $ k \in \Z_{p-1} $ be a random number and $ x \in \Z_p^{\ast} $ the 
plaintext. \\
\underline{Encryption:}
\[ e_T(x,k)=(y_1,y_2), \]
where
\[ y_1=\alpha^k \mod p\]
and
\[ y_2 = x\beta^k \mod p.\]
\underline{Decryption:}
\[ d_T(y_1,y_2)= y_2 (y_1^{a})^{-1} \mod p \]
}}
\end{center}

@@

   \bibitem[Adleman1982]{Adleman1982} \index{Adleman 1982}
       Adleman L.: 
       \emph{On breaking the iterated Merkle-Hellman public key 
             Cryptosystem.} \\ 
       Advances in Cryptology, Proceedings of Crypto 82, 
       Plenum Press 1983, 303-308.

   \bibitem[Balcazar1988]{Balcazar1988} \index{Balcazar 1988} 
       Balcazar J.L., Daaz J., Gabarr\'{} J.: 
       \emph{Structural Complexity I.} \\ 
       Springer Verlag, pp 63.

    \bibitem[Brickell1985]{Brickell1985} \index{Brickell 1985}
       Brickell E.F.:
       \emph{Breaking Iterated Knapsacks.}  \\
       Advances in Cryptology: Proc. CRYPTO\'84, 
       Lecture Notes in Computer Science, vol. 196, 
       Springer-Verlag, New York, 1985, pp. 342-358.

    \bibitem[Lagarias1983]{Lagarias1983} \index{Lagarias 1983} 
       Lagarias J.C.:
       \emph{Knapsack public key Cryptosystems and diophantine
             Approximation.} \\
       Advances in Cryptology, Proseedings of Crypto 83, Plenum Press.

    \bibitem[Merkle1978]{Merkle1978} \index{Merkle 1978} 
       Merkle R. and Hellman M.:
       \emph{Hiding information and signatures in trapdoor knapsacks.} \\
       IEEE Trans. Information Theory, IT-24, 1978.

    \bibitem[RSA1978]{RSA1978} \index{RSA 1978}
       Rivest R.L., Shamir A. and Adleman L.:
       \emph{A Method for Obtaining Digital Signatures and 
             Public Key Cryptosystems.} \\
       Commun. ACM, vol 21, April 1978, pp. 120-126.

    \bibitem[Shamir1982]{Shamir1982} \index{Shamir 1982}
       Shamir A.:
       \emph{A polynomial time algorithm for breaking the basic 
             Merkle-Hellman Cryptosystem.} \\
       Symposium on Foundations of Computer Science (1982), 145-152.

%already defined in elementaryNumberTheory.tex
    \bibitem[Stinson1995]{4Stinson1995} \index{Stinson 1995}
       Stinson D.R.:
       \emph{Cryptography.} \\
       CRC Press, Boca Raton, London, Tokyo, 1995.

>>>>

\newpage
%**************************************************************************************************************************
\section{The Mathematical Ideas behind Modern Cryptography}
\label{Chapter_ModernCryptography}
\hypertarget{Chapter_ModernCryptography}{}
%**************************************************************************************************************************
(Oyono R. / Esslinger B., Sep. 2000, Updates Nov. 2000, Feb. 2003)

%--------------------------------------------------------------------------------------------------------------------------
\subsection{One way functions with trapdoor and complexity classes}
%--------------------------------------------------------------------------------------------------------------------------
\index{Cryptography!modern} \index{One way function} \hypertarget{OneWayFunktion1}{}
A {\bf one way function} is a function that can be calculated 
efficiently, but whose inverse is extremely complicated and practically 
impossible to calculate.\par

@@

%--------------------------------------------------------------------
\subsubsection{Merkle-Hellman knapsack encryption}
%--------------------------------------------------------------------
\index{Hellman, Martin} \index{Merkle, Ralph}

@@

In 1982, \index{Shamir, Adi} Shamir \cite{Shamir1982} specified an algorithm for 
breaking the system in polynomial \index{Polynomial} time without solving the general knapsack 
problem. Len \index{Adleman, Leonard} Adleman \cite{Adleman1982} and Jeff 
Lagarias \index{Lagarias, Jeff} \cite{Lagarias1983} specified an algorithm for 
breaking the twice iterated Merkle-Hellman knapsack encryption procedure in 
polynomial time. Ernst Brickell \index{Brickell, Ernst} \cite{Brickell1985} then 
specified an algorithm for breaking multiply iterated Merkle-Hellman knapsack 
encryption procedures in polynomial time. This made this procedure unsuitable as 
an encryption procedure. It therefore delivers a one way function whose trapdoor 
information (defamiliarisation of the 0-1 knapsack problem) could be discovered 
by an evesdropper.

@@

%--------------------------------------------------------------------
\subsubsection[The RSA procedure]
{The RSA procedure\footnotemark}
\footnotetext{
Using CrypTool\index{CrypTool} you can gain practical experience
with the RSA procedure via the menu {\bf Indiv.Procedures \textbackslash{} 
RSA Cryptosystem \textbackslash{} RSA Demonstration}.
}
\index{RSA} \hypertarget{RSAVerfahren}{} 
As early as 1978, R. \index{Rivest, Ronald} Rivest, \index{Shamir, Adi} A. Shamir,
\index{Adleman, Leonard} L. Adleman \cite{RSA1978} introduced 
the most important asymmetric cryptography procedure to date.  \par

@@

In this case it has been shown that the procedure \index{Rabin, Michael O.} 
\index{Rabin!public key procedure} is equivalent to breaking the factorisation problem. 
Unfortunately, this procedure is susceptible to chosen-cipher text attacks.
\index{Attack!chosen-cipher text}
\begin{center}
\fbox{\parbox{12cm}{        
Let $ p $ and $ q $ be two different prime numbers with $ p,q\equiv 3 \mod 4 $ 
and $ n = pq.$ Let $ 0\leq B \leq n-1.$ \\
\underline{Public key:}
\[ e=(n,B). \]
\underline{Private key:}
\[ d=(p,q). \]
\underline{Encryption:}
\[ y= e_{T} (x) = x(x+B) \mod n.\]
\underline{Decryption:}
\[ d_{T} (y) = \sqrt{y + B^2/4} -B/2 \mod n. \]
}}
\end{center}

@@

    \subsubsection{The discrete logarithm in $ \Z_p $}
Let $ p $ be a prime number and let $ g \in \Z_p^\ast=\{0,1,\ldots,p-1\} $. Then 
the discrete exponential function base $ g $  is defined as
\[ e_g : k \longrightarrow y:=g^k \mod p, \quad 1\leq k \leq p-1. \]
The inverse function is called a discrete logarithm function $ \log_g $; the 
following holds:
\[ \log_g (g^k) =k. \]
\index{Exponential function!discrete} The problem of the discrete logarithm (in 
$ \Z_p^\ast$) is understood to be as follows:
\[ {\rm Given~ } p,g {\rm ~and~ } y, {\rm~determine~} k {\rm ~such~that~ } 
y=g^k \mod p {\rm .}\]
It is much more difficult to calculate the discrete logarithm than to evaluate 
the discrete exponential function (see chapter \ref{MultOrdPrimitveRoot}).
There are several procedures for calculating the discrete logarithm 
\cite{4Stinson1995}\index{Stinson 1995}:
\vskip + 5pt
\begin{center}
\begin{tabular}{|l|l|}\hline
Name                 &        Complexity \\ \hline \hline
Baby-Step-Giant-Step &         $ O(\sqrt{p}) $ \\ \hline
Silver-Pohlig-Hellman    &    polynomial in $ q, $ the greatest \\
&  prime factor of $ p-1. $ \\ \hline
Index-Calculus &             $ O(e^{(1+o(1)) \sqrt{\ln (p) \ln (\ln (p))}}) $ \\ 
\hline
\end{tabular}
\end{center}
\vskip +5 pt
\index{Silver} \index{Pohlig, S. C.} \index{Hellman, Martin}
\index{Baby-Step-Giant-Step}

%--------------------------------------------------------------------
\subsubsection[Diffie-Hellman key agreement]
{Diffie-Hellman key agreement\footnotemark}
\footnotetext{%
With CrypTool\index{CrypTool} this exchange protocol has been
visualized: you can execute the single steps with concrete numbers using 
menu {\bf Indiv. Procedures \textbackslash{} Protocols \textbackslash{} Diffie-Hellman Demonstration}.
}

\index{Key agreement (key exchange)!Diffie-Hellman} 
\index{Diffie, Whitfield}
\index{Hellman, Martin}
\index{Diffie-Hellman}
\hypertarget{DH-KeyExch}{} \label{DH-KeyExch}

@@

%--------------------------------------------------------------------
\subsubsection{ElGamal public key encryption procedure in $ \Z_p^\ast$}
%--------------------------------------------------------------------
\index{ElGamal!public key}
By varying the Diffie-Hellman key agreement protocol \index{Diffie-Hellman} 
\index{Encryption!ElGamal public key} slightly, you can obtain an 
asymmetric encryption algorithm. This observation was made by Taher ElGamal.
\begin{center}
\fbox{\parbox{12cm}{        
Let $ p $ be a prime number such that the discrete logarithm in $ \Z_p $ is 
difficult to compute. Let $ \alpha \in \Z_p^\ast $ be a primitive element. Let $a \in \N$ and $ 
\beta = \alpha^{a}  \mod p. $\\
\underline{Public key:}
\[ p,\alpha,\beta. \]
\underline{Private key:}
\[a. \]
Let $ k \in \Z_{p-1} $ be a random number and $ x \in \Z_p^{\ast} $ the 
plaintext. \\
\underline{Encryption:}
\[ e_T(x,k)=(y_1,y_2), \]
where
\[ y_1=\alpha^k \mod p\]
and
\[ y_2 = x\beta^k \mod p.\]
\underline{Decryption:}
\[ d_T(y_1,y_2)= y_2 (y_1^{a})^{-1} \mod p \]
}}
\end{center}

@@

   \bibitem[Adleman1982]{Adleman1982} \index{Adleman 1982}
       Adleman L.: \\ 
       \emph{On breaking the iterated Merkle-Hellman public key 
             Cryptosystem.} \\ 
       Advances in Cryptology, Proceedings of Crypto 82, 
       Plenum Press 1983, 303-308.

   \bibitem[Balcazar1988]{Balcazar1988} \index{Balcazar 1988} 
       Balcazar J.L., Daaz J., Gabarr\'{} J.: \\ 
       \emph{Structural Complexity I.} \\ 
       Springer Verlag, pp 63.

    \bibitem[Brickell1985]{Brickell1985} \index{Brickell 1985}
       Brickell E.F.: \\
       \emph{Breaking Iterated Knapsacks.}  \\
       Advances in Cryptology: Proc. CRYPTO\'84, 
       Lecture Notes in Computer Science, vol. 196, 
       Springer-Verlag, New York, 1985, pp. 342-358.

    \bibitem[Lagarias1983]{Lagarias1983} \index{Lagarias 1983} 
       Lagarias J.C.: \\
       \emph{Knapsack public key Cryptosystems and diophantine
             Approximation.} \\
       Advances in Cryptology, Proseedings of Crypto 83, Plenum Press.

    \bibitem[Merkle1978]{Merkle1978} \index{Merkle 1978} 
       Merkle R. and Hellman M.: \\
       \emph{Hiding information and signatures in trapdoor knapsacks.} \\
       IEEE Trans. Information Theory, IT-24, 1978.

    \bibitem[RSA1978]{RSA1978} \index{RSA 1978}
       Rivest R.L., Shamir A. and Adleman L.: \\
       \emph{A Method for Obtaining Digital Signatures and 
             Public Key Cryptosystems.} \\
       Commun. ACM, vol 21, April 1978, pp. 120-126.

    \bibitem[Shamir1982]{Shamir1982} \index{Shamir 1982}
       Shamir A.: \\
       \emph{A polynomial time algorithm for breaking the basic 
             Merkle-Hellman Cryptosystem.} \\
       Symposium on Foundations of Computer Science (1982), 145-152.

%already defined in elementaryNumberTheory.tex
    \bibitem[Stinson1995]{4Stinson1995} \index{Stinson 1995}
       Stinson D.R.: \\
       \emph{Cryptography.} \\
       CRC Press, Boca Raton, London, Tokyo, 1995.
